\documentclass[letterpaper,11pt]{article}

\usepackage{fontspec}
\usepackage{xeCJK}
\setCJKmainfont{Noto Serif CJK JP}

\usepackage{enumitem}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSingleItem}[1]{
  \item\small{
    \textbf{#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingEDU}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} &\textit{\small #4} \\
      \textit{\small #5}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingProjects}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small#2}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingExperience}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small#2}\\
      \textit{\small#3}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingProjectsSingle}[1]{
  \vspace{-1pt}\item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, labelsep=4pt]}

\newcommand{\resumeSubHeadingEDUSTART}{\begin{itemize}[leftmargin=*, itemindent=0pt, labelsep=0.5em]}

\newcommand{\resumeSubHeadingEDUEND}{\end{itemize}}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSingleItemListStart}{\begin{itemize}}
\newcommand{\resumeSingleItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Nicholas Brezinski}} & Email : \href{mailto:nicholashbrezinski@gmail.com}{nicholashbrezinski@gmail.com}\\
  \href{http://sourabhbajaj.com/}{https://nickbrezinski.com} & Mobile : +1 (617) 402-0897 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingEDUSTART
    \resumeSubheadingEDU{University of North Carolina at Charlotte}{Charlotte, NC}{Bachelor of Computer Science \& Minor in Japanese Studies;  GPA: 3.23}{Aug. 2021 -- May. 2025}{Computing and Informatics Dean's List 4x}
    \resumeSubheading
      {Sophia University}{Tokyo, Japan}
      {Study Abroad (Japanese Studies)}{March. 2024 -- Aug. 2024}
    \resumeSubheading
      {150-Hour CIEE TEFL Certification}{CIEE, Online}
      {Certification in Teaching English as a Foreign Language (TEFL)}{Jan. 2025 -- May. 2025}
  \resumeSubHeadingEDUEND



%-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheadingProjects{Fortnite Drop Calculator}{Apr. 2025 - Present}
      \resumeItemListStart
        \resumeSingleItem{Developed a web-based tool using TypeScript, Next.js, and Tailwind CSS to calculate the mathematically most optimal jump point in Fortnite, reducing total travel time by simulating bus path, fall physics, and glider deployment.}
        
        \resumeSingleItem{Custom simulation algorithm to compute precise drop and glide trajectories, integrating interactive map visualizations and UI components for competitive player utility.}
      \resumeSingleItemListEnd

    \resumeSubheadingProjects{辞典書 (Japanese Dictionary App)}{Mar. 2025 - Present}
      \resumeItemListStart
        \resumeSingleItem{Cross-platform Japanese dictionary and language learning app using React Native, Expo, and TypeScript, featuring comprehensive dictionary search, spaced repetition study system with Anki SM2 algorithm, pitch accent visualization, and audio pronunciation capabilities for enhanced learning experience.}
        
        \resumeSingleItem{Study features and progress tracking including JLPT level goal setting, personalized study metrics, daily word recommendations, and intelligent spaced repetition scheduling that adapts to user performance, resulting in a comprehensive language learning platform.}
      \resumeSingleItemListEnd

      \resumeSubheadingProjects{ClimbSight (Rock Climbing Analysis Application)}{Mar. 2025 - Present (On Break)}
      \resumeSingleItemListStart
        \resumeSingleItem{Full-stack web application leveraging MediaPipe computer vision and Google AI to provide real-time pose detection and biomechanical analysis for rock climbing, featuring video recording with skeletal overlay visualization, advanced motion tracking algorithms, and automated hold detection using image processing techniques.}
      \resumeSingleItemListEnd

    \resumeSubheadingProjects{LanGAPP}{May. 2023 - Jun. 2023}
      \resumeItemListStart
        \resumeSingleItem{Developed a real-time vocal translation tool (English to Japanese/ Spanish) using Python, NLP, speech-to-text, and text-to-speech APIs, improving voice output with natural cadence via neural network models.}
        
        \resumeSingleItem{Integrated AI-based language processing and Dockerized deployment to deliver fast, user-friendly spoken translation through a microphone input interface.}
      \resumeSingleItemListEnd
\resumeSubHeadingListEnd
%----------Experience-----------------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheadingExperience{Floor Staff}{May. 2025 - Present}{Triangle Rock Club Morrisville}
      \resumeItemListStart
        \resumeSingleItem{Developed a real-time vocal translation tool (English to Japanese/ Spanish) using Python, NLP, speech-to-text, and text-to-speech APIs, improving voice output with natural cadence via neural network models.}
      \resumeSingleItemListEnd

%*
  
%
  \resumeSubHeadingListEnd
%

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Technical Skills}{: Python, JavaScript, TypeScript, SQL, Java, Dart, React/ ReactJS, Flutter, Vite, Supabase, Node.js, Tailwind CSS, shadcn/ui, Mediapipe, Jupyter Notebook, Google Colab, Scikit-learn, Pandas, Seaborn, Hypothesis Testing, Git, Firebase, Figma}
    \item{
        \textbf{Soft Skills}{: Project Management, Problem Solving \& Debugging, Public Speaking, Bilingual Communication, Japanese, English, Teaching, TEFL Certification}
    } 
     
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
